The Impact of Model Assumptions on RES Drought Analysis

### 2024-11-14 Article/main.tex
Add comments to discussion

This study has highlighted the key differences between the three datasets: Atlite, C3S-E G, and C3S-E N in their ability to model RES droughts. One of the most significant differences is how each dataset incorporates the specific locations of RES farms. Both Atlite and C3S-E G take into account the exact locations of wind and PV farms, which should, in theory, provide a more accurate representation of RES generation. However, our analysis shows that the Atlite dataset generally performs better, particularly in its wind generation estimates, where it closely follows the EirGrid data. This suggests that while the inclusion of RES farm locations is important, the accuracy of the CF modeling used by Atlite may be the determining factor in its superior performance.

When analysing the results, we found that the two C3S-E datasets (C3S-E G and C3S-E N) consistently show similar outcomes across various figures (Fig.~\ref{fig:boxplot_number_events},~\ref{fig:return_periods},~\ref{fig:res_droughts_seasonality}), suggesting that their differences in methodology have minimal impact on the results. In contrast, Atlite stands out, in its ability to model wind generation, as evidenced by the more accurate correlation with EirGrid data seen in the verification process (Section \ref{sec:wind_verification}). This distinction is further underscored in the figures, where Atlite often reports higher or more accurate return periods and a greater number of RES droughts (Fig.~\ref{fig:boxplot_number_events},~\ref{fig:return_periods}), particularly in scenarios with increased PV capacity.

One of the most critical conclusions of this study is that the specific locations of RES farms, while important, have less impact on the accuracy of RES drought modeling than the precision of the CF models themselves. Atlite's superior performance suggests that refining these models could lead to better forecasting and planning for RES droughts, which is crucial for energy security.

Looking to the balanced scenario, our analysis suggests a significant shift in the dynamics of RES droughts due to the anti-correlation between wind and PV generation. This scenario reveals the importance of seasonality in RES droughts (Fig.~\ref{fig:res_droughts_seasonality}), where a diversified energy portfolio that includes both wind and PV could decrease the frequency and duration of RES droughts.

For policymakers, the findings of this study highlight the risks of inadequate modeling and planning. Accurate RES drought forecasting is essential for ensuring energy security, especially as Ireland moves toward an ambitious renewable energy target.

In terms of future research, there are two main topics to explore. First, integrating future climate data with energy scenarios to better understand how climate change might affect RES droughts. Second, expanding the scope of the study to include Europe, would provide a more comprehensive understanding of RES drought in an interconnected energy grid. However, this expansion would require extensive verification across all EU countries, making it a more complex but highly relevant challenge.

>>>>

This study has highlighted the key differences between the three datasets: Atlite, C3S-E G, and C3S-E N in their ability to model RES droughts. One of the most significant differences is how each dataset incorporates the specific locations of RES farms. Both Atlite and C3S-E G take into account the exact locations of wind and PV farms, which should, in theory, provide a more accurate representation of RES generation. However, our analysis shows that the Atlite dataset generally performs better, particularly in its wind generation estimates, where it closely follows the EirGrid data. This suggests that while the inclusion of RES farm locations is important, the accuracy of the CF modeling \textcolor{magenta}{I would say power curve model instead of CF modelling} used by Atlite may be the determining factor in its superior performance.\textcolor{magenta}{Superior how? Is finding more droughts superior or is it reproducing reality? I reckon it's the second, but make it explicit. Also, there is no explicit mention of PV, if you mention wind explicitly (which I agree on doing) I would add PV. Even though it is replacing that "However" with "Even though this is true for PV, our analysis shows that for wind..."}

When analysing the results, we found that the two C3S-E datasets (C3S-E G and C3S-E N) consistently show similar outcomes across various figures \textcolor{magenta}{I would not refer to them as figures, but as analysis or something like that. But if you do choose the word analysis, do not start the sentence with "When analysing the results..." and instead use something like "The results show..."} (Fig.~\ref{fig:boxplot_number_events},~\ref{fig:return_periods},~\ref{fig:res_droughts_seasonality}), suggesting that their differences in methodology have minimal impact on the results. In contrast, Atlite stands out in its ability to model wind generation, as evidenced by the more accurate correlation with EirGrid data seen in the verification process (Section \ref{sec:wind_verification}). This distinction is further underscored in the figures \textcolor{magenta}{Same as before, avoid referring to the figures. We do not discuss the result (that was done in results), we discuss what it implies}, where Atlite often reports higher or more accurate return periods and a greater number of RES droughts (Fig.~\ref{fig:boxplot_number_events},~\ref{fig:return_periods}), particularly in scenarios with increased PV capacity. \textcolor{magenta}{For me, the point of this paragraph is quite clear but does not really come across at the moment: Atlite is the best one at reproducing reality (as established in the previous paragraph). At the same time, a long-term analysis shows more droughts for Atlite than any other model. This means that model selection is key to correctly quantify the risk and avoid undersizing the reserve capacity.}

One of the most critical conclusions of this study is that the specific locations of RES farms, while important, have a lower impact on the accuracy of RES drought modelling than the precision of the CF models themselves. \textcolor{magenta}{Same as before, I would not refer to CF models, but instead wind power curve and PV panel models} Atlite's superior performance suggests that refining these models could lead to better forecasting and planning for RES droughts, which is crucial for energy security.

Looking to the balanced scenario, our analysis suggests a significant shift in the dynamics of RES droughts due to the anti-correlation between wind and PV generation. This scenario reveals the importance of seasonality in RES droughts (Fig.~\ref{fig:res_droughts_seasonality}), where a diversified energy portfolio that includes both wind and PV could decrease the frequency and duration of RES droughts.
\textcolor{magenta}{I would merge these two paragraphs into one. Here are my thoughts in order: 1. We have found how wind and PV together perform better than individually in terms of droughts. 2. A specific mention of seasonality and how it is reduced. 3. Mention how Ireland has a very wind-dependent system and how targets for PV are ambitious in the coming years, almost making wind and PV capacities equal (maybe not the phrasing but you see the point, putting forward the balance again). 4. Link to policymakers in terms of how meeting targets of installed capacity can help improve the energy security thanks to this diversification. 5. Close with the importance of the right model selection for RES drought assessment, especially as more renewable capacity comes into the system.}
For policymakers, the findings of this study highlight the risks of inadequate modelling and planning. Accurate RES drought forecasting is essential for ensuring energy security, especially as Ireland moves toward an ambitious renewable energy target.

In terms of future research, there are two main topics to explore. First, integrating future climate data with energy scenarios to better understand how climate change might affect RES droughts. Second, expanding the scope of the study to include Europe would provide a more comprehensive understanding of RES drought in an interconnected energy grid. However, this expansion would require extensive verification across all EU countries, making it a more complex but highly relevant challenge.
